---
title: "Lab3"
author: "Diana Dewald, Eliott Doyle"
date: "1/31/2022"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rio)
library(here)
library(colorBlindness)

honey <- import(here("honeyproduction.csv"))
#View(honey)
```

# 1. Visualize the total production of honey across years by state. Use color to highlight the west coast (Washington, Oregon, and California) with a different color used for each west coast state.

```{r q1, echo = FALSE, warning = FALSE, message = FALSE}
honeyplot <- honey %>% 
  ggplot(aes(x = totalprod,
             y = reorder(state, totalprod))) +
  geom_col(fill = "goldenrod2",
           alpha = .8) +
  geom_col(data = filter(honey,
                           state == "OR"),
           fill = "khaki1") +
  geom_col(data = filter(honey,
                           state == "WA"),
           fill = "aquamarine4") +
  geom_col(data = filter(honey,
                           state == "CA"),
           fill = "cadetblue3") +
  theme_classic() +
  labs(
    title = "Honey production by US state",
    x = "Total Honey Production",
    y = "State") 

honeyplot
```

# 2. Reproduce the plot according three different kinds of color blindness, as well as a desaturated version.

```{r q2, echo = FALSE, warning = FALSE, message = FALSE}
colorBlindness::cvdPlot(honeyplot)
```

# 3. Reproduce the plot using a color blind safe palette.

```{r q3, echo = FALSE, warning = FALSE, message = FALSE}
#making a new df with a column for region that I will use for my palette
honey_new <- honey
region <- data.frame(state = c('CA', 'OR', 'WA'),
                     region = c('CA', 'OR', 'WA'))
honey_new <- left_join(honey_new, region, by = "state")
honey_new[["region"]][is.na(honey_new[["region"]])] <- "Other"
#View(honey_new)

#palette I want to use:
cbbPalette <- c("#000000", "#E69F00", "#F0E442","#009E73", "#0072B2", "#D55E00", "#CC79A7")

honeyplot_cb <- honey_new %>% 
  ggplot(aes(x = totalprod,
             y = reorder(state, totalprod))) +
  geom_col(aes(fill = region),
           alpha = .9) +
  scale_fill_manual(values=cbbPalette) +
  theme_classic() +
  labs(
    title = "Honey production by US state",
    x = "Total Honey Production",
    y = "State") 

honeyplot_cb


colorBlindness::cvdPlot(honeyplot_cb)
```

# 4. Download the file here denoting the region and division of each state.
* Join the file with your honey file 
* Produce a bar plot displaying the average honey for each state (collapsing across years).
* Use color to highlight the region of the country the state is from.
* Note patterns you notice.

# 5. Create a heatmap displaying the average honey production across years by region (averaging across states within region).

# 6. Create at least one more plot of your choosing using color to distinguish, represent data values, or highlight.



